### 2018-07-11 FrascatiPlot/Paper/NucleiB2.tex
Minor fixes to comments before going  for pizza. Also added a reference to Braaten. We continue tomorrow.

\begin{abstract}
(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at LHC energies. At LHC energies, their production is typically discussed within the framework of coalescence and thermal-statistical production models. While it is often argued that both approaches are not distinguishable, we present a detailed study of both theories which reveals large differences between the two scenarios for the production of objects with extended wave-functions. Both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, but they consequently largely differ in their description of (anti-)hyper-triton production.
%Confronting our results with recent ALICE measurements, the coalescence approach is found to provide a correct description of the data only in small systems such as pp collisions, while it fails for central Pb--Pb collisions. 
The thermal-statistical model is found to be in agreement with results in central Pb--Pb collisions even though such fragile objects should be destroyed in hadronic interactions after the chemical freeze-out of the system. Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a discussion basis for more refined calculations in the future.
\end{abstract}

@@

\section{Introduction} 
The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these collisions. In addition, these studies might shed light on the internal structure of the formed objects themselves. 
In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, protons, kaons, etc.), because their size (i.e. the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.  
The relevant known properties of the objects under study here are summarised in Table \ref{tab:nucleusradii}.
As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments. Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects. Theoretical calculations indicate a rms of the wave-function of the hyper-triton of about 5 fm which is significantly larger than that of non-strange $A$ = 3 nuclei. This is driven by the average separation of the Lambda with respect to the two other nucleons which is expected to amount up to 10 fm. In principle, halo nuclei as $^{6}$He would therefore be ideal for such studies, but they remain out of the experimental reach in high-energy experiments in the near future.

@@

\centering
\begin{tabularx}{\textwidth}{cccccccc}
%\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} 
 \hline \hline
\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & \makecell{Spin \\$J_{A}$} & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs. \\ \hline
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}      \\ \hline
\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\ \hline
\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\ \hline \hline
\end{tabularx}
\caption{Properties of nuclei and hyper-nuclei. $B_{E}$ is the binding energy in MeV. The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction, \rmsradius. The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced. Details are given in Appendix \ref{appendix:Sato}. Please note that proton rms charge radius $\lambda_{p}$ is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
 References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
\label{tab:nucleusradii}
\end{table}

To this purpose, we compare to models the existing data from the Large Hadron Collider. For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size. 
In the nucleon-coalescence approach, nuclei are formed at kinetic freeze-out by coalescence of nucleons that are nearby in space and have similar velocities. The coalescence model is reviewed in Section \ref{sec:coalescence}, starting from its simplest form (uncorrelated nucleon emission from a point-like source) to the full space-time evolution picture as discussed in \cite{Scheibl:1998tk}. In section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as an alternative approach. 
The direct comparison of the two approaches and the comparison with data are discussed in section \ref{sec:comparison}.
We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches. 
A comparison of the production rates of nuclei with similar mass but very different internal structure has already been suggested for the case of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}. However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
In section \ref{sec:projections}, we propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 and 4, in order to rule out or support the aforementioned scenarios. As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity to for the final understanding of (anti-)(hyper-)nuclei production.
Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss} and future \cite{AMS100, Aramaki:2015laa} experiments. 
In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.

@@

\subsection{Full coalescence}
\label{subsec:FullCoalescence}

@@

This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions. In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter of the harmonic oscillator potential, $r_{A}$. The approximation of the wave-function with a gaussian form can be further refined with more realistic parameterisations, e.g. the Hulthen parameterisation for the deuteron or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}. We encourage future more rigorous numerical studies which address the coalescence probabilities with more realistic wave-functions, but remain with the gaussian ansatz in the following in order to obtain more intuitive analytic solutions which highlight the sensitivity to the source (i.e. the centrality dependence) and the (hyper-)nucleus size. \textcolor{red}{Consider mentioning the further  approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}

@@

\begin{equation}
\langle C_{d} \rangle \approx \frac{1}{\left[1+ \left(\frac{\dradius}{2R_{\perp}(m_{T})}\right)^{2}\right] \sqrt{1+ \left(\frac{\dradius}{2R_{\|}(m_{T})}\right)^{2}}}
\label{eq:Cd}
\end{equation}
%
where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
The size of the nucleus enters in the determination of the coalescence parameter \btwo~via the quantum-mechanical correction factor $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})}
\label{eq:B2cd}
\end{equation}
%
which is the main result of \cite{Scheibl:1998tk}. It is interesting to note that the coalescence parameter decreases with increasing volume, as expected. In addition to this, the quantum mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability. 
If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to 
\begin{equation}
\langle C_{d} \rangle \approx \left[1+ \left(\frac{\dradius}{2R(m_{T})}\right)^{2}\right]^{-3/2}
\label{eq:Cdapprox}
\end{equation}
%
and
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}R^{3}(m_{T})}.
\label{eq:B2approx}
\end{equation}
%
Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo (on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm similar to the value currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm. 
As can be seen in Fig. \ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.

@@

\subsection{Source volume}
\label{SecSourceVolume}
As in \cite{Scheibl:1998tk}, we identify the source volume as the effective sub-volume of the whole system which is governed by the homogeneity length of the interacting nucleons. In addition, the same authors claim that this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry. 
The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation. As discussed in Appendix \ref{appendix:YKP}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$, thus $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\textwidth]{HbtRadiusParam.eps}
\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Abelev:2012sq}.}
\label{fig:radiiparam}
\end{center}
\end{figure}

- excess binding energy needs to be released to the system to make coalescence work

@@

In the statistical-thermal approach, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to the chemical freeze-out temperature $T_{chem}$ due to their large mass $m$ and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$. As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
In contrast to the coalescence approach, the current implementations~\cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} of the statistical-thermal model provide only \pt-integrated yields and not the full hadron spectra. 
In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization. When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit of the pion, kaon and proton spectra measured in each collision system and multiplicity event class by ALICE~\cite{Abelev:2013vea}. 
The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}. 
This choice is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013xaa,Abelev:2013vea} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}. Based on the thus obtained spectra, we calculate the corresponding coalescence parameters for a given \pt/A and compare it with coalescence expectations. Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality/multiplicity classes, we use the corresponding \avdNdeta~in the same class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}. 
In contrast to the coalescence approach which explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model, which as a simplified hydrodynamic model treats the system based as a continuum and is not particle based. The thermal model on the other hand, implements eigenvolume corrections where the object radius is fixed as an external parameter ($r=0.3$~fm in the case of baryons for the GSI-Heidelberg prediction used here). We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.

@@

Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017,ALICE:deuteronflow2017,Adam:2015yta}. 
In Fig. \ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter \btwo~from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) with the ALICE data.  
First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} is used to map the \avdNdeta~to the source size (datapoints shown in the two left panels).
We notice already at this point that the coalescence volume from our extracted parameterisation of the HBT radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo.

@@

 \subsection{Thermal and coalescence model for A=2,3 anti- and hyper-nuclei}

>>>>

\begin{abstract}
(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at LHC energies. At LHC energies, their production is typically discussed within the framework of coalescence and thermal-statistical production models. While it is often argued that both approaches are not distinguishable, we present a detailed study of both theories which reveals large differences between the two scenarios for the production of objects with extended wave-functions. Both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, but they consequently largely differ in their description of (anti-)hyper-triton production.
%Confronting our results with recent ALICE measurements, the coalescence approach is found to provide a correct description of the data only in small systems such as pp collisions, while it fails for central Pb--Pb collisions. 
The thermal-statistical model is found to be in agreement with results in central Pb--Pb collisions even though fragile objects such as light (anti-)(hyper-)nuclei should be destroyed in hadronic interactions after the chemical freeze-out of the system. Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a discussion basis for more refined calculations in the future.
\end{abstract}

@@

\section{Introduction} 
The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these collisions. In addition, these studies might shed light on the internal structure of the formed objects themselves. 
In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, protons, kaons, etc.), because their size (i.e. the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.  
The relevant known properties of the objects under study here are summarised in Table \ref{tab:nucleusradii}.
As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments. Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects. Theoretical calculations indicate a rms of the wave-function of the hyper-triton of about 5 fm \cite{Nemura:1999qp} which is significantly larger than that of non-strange $A$ = 3 nuclei. This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount up to 10 fm. In principle, halo nuclei as $^{6}$He would therefore be ideal for such studies, but they remain out of the experimental reach in high-energy experiments in the near future.

@@

\centering
\begin{tabularx}{\textwidth}{cccccccc}
%\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} 
 \hline \hline
\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & \makecell{Spin \\$J_{A}$} & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs. \\ \hline
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}      \\ \hline
\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\ \hline
\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\ \hline \hline
\end{tabularx}
\caption{Properties of nuclei and hyper-nuclei. $B_{E}$ is the binding energy in MeV. The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction, \rmsradius. The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced. Details are given in Appendix \ref{appendix:Sato}. Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents. Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.
 References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
\label{tab:nucleusradii}
\end{table}

To this purpose, we compare to models the existing data from the Large Hadron Collider. For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size. 
In the nucleon-coalescence approach, nuclei are formed at kinetic freeze-out by coalescence of nucleons that are nearby in space and have similar velocities. The coalescence model is reviewed in Section \ref{sec:coalescence}, starting from its simplest form (uncorrelated nucleon emission from a point-like source) to the full space-time evolution picture as discussed in \cite{Scheibl:1998tk}. In section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as an alternative approach. 
The direct comparison of the two approaches and the comparison with data are discussed in section \ref{sec:comparison}.
We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches. 
A comparison of the production rates of nuclei with similar mass but very different internal structure has already been suggested for the case of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}. However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 and 4, in order to rule out or support the aforementioned scenarios. As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity to for the final understanding of (anti-)(hyper-)nuclei production.
Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss} and future \cite{AMS100, Aramaki:2015laa} experiments. 
In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.

@@

\subsection{Advanced coalescence}
\label{subsec:FullCoalescence}

@@

This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions. In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter of the harmonic oscillator function, $r_{A}$. The approximation of the wave-function with a gaussian form can be further refined with these more realistic parameterisations, e.g. the Hulthen parameterisation for the deuteron or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}. We encourage future more rigorous numerical studies which address the coalescence probabilities with more realistic wave-functions, but remain with the gaussian ansatz in the following in order to obtain more intuitive analytic solutions which highlight the sensitivity to the source (i.e. the centrality dependence) and the (hyper-)nucleus size. \textcolor{red}{Consider mentioning the further  approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}

@@

\begin{equation}
\langle C_{d} \rangle \approx \frac{1}{\left[1+ \left(\frac{\dradius}{2R_{\perp}(m_{T})}\right)^{2}\right] \sqrt{1+ \left(\frac{\dradius}{2R_{\|}(m_{T})}\right)^{2}}}
\label{eq:Cd}
\end{equation}
%
where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
The size of the nucleus enters in the determination of the coalescence parameter \btwo~via the quantum-mechanical correction factor $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})}
\label{eq:B2cd}
\end{equation}
%
which is the main result of \cite{Scheibl:1998tk}. It is interesting to note that the coalescence parameter decreases with increasing volume, as expected. In addition to this, the quantum mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability. 
If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to 
\begin{equation}
\langle C_{d} \rangle \approx \left[1+ \left(\frac{\dradius}{2R(m_{T})}\right)^{2}\right]^{-3/2}
\label{eq:Cdapprox}
\end{equation}
%
and
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}R^{3}(m_{T})}.
\label{eq:B2approx}
\end{equation}
%
Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm similar to the value currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm. 
As can be seen in Fig. \ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.

@@

\subsection{Source volume}
\label{SecSourceVolume}
As in \cite{Scheibl:1998tk}, we identify the source volume as the effective sub-volume of the whole system which is governed by the homogeneity length of the interacting nucleons. In addition, the same authors claim that this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry. 
The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation. As discussed in Appendix \ref{appendix:YKP}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$. We then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{HbtRadiusParam.eps}
\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Abelev:2012sq}.}
\label{fig:radiiparam}
\end{center}
\end{figure}

%- excess binding energy needs to be released to the system to make coalescence work

@@

In the statistical-thermal approach, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to the chemical freeze-out temperature $T_{chem}$ due to their large mass $m$ and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$. As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
In contrast to the coalescence approach, the current implementations~\cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} of the statistical-thermal model provide only \pt-integrated yields and not the full hadron spectra. 
In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization. When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit of the pion, kaon and proton spectra measured in each collision system and multiplicity event class by ALICE~\cite{Abelev:2013vea}. 
The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}. 
This choice, as opposed to using ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013xaa,Abelev:2013vea} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}. Based on the thus obtained spectra, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations. Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality/multiplicity classes, we use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}. 
In contrast to the coalescence approach which explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model, which as a simplified hydrodynamic model treats the system as a continuum and is not particle based. The thermal model on the other hand, implements eigenvolume corrections where the object radius is fixed as an external parameter ($r=0.3$~fm in the case of baryons for the GSI-Heidelberg model used here). We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.

@@

Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017,ALICE:deuteronflow2017,Adam:2015yta}. 
In Fig. \ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter \btwo~from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) with the ALICE data.  
First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} is used to map the \avdNdeta~to the source size (datapoints shown in the two left panels).
We notice already at this point that the coalescence volume from our extracted parameterisation of the HBT radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.

@@

 \subsection{Thermal and coalescence model for A = 2, 3 anti- and hyper-nuclei}

In figure~\ref{fig:CompareThermalAndCoalescence}, the data available data for (anti-)deuterons, (anti)\hethree\ and \hthreelambda~\cite{Adam:2015yta} is compared to both coalescence and thermal model predictions. For the coalescence predictions, the radius parameterisation tuned to the data is used. The combined thermal model and blast-wave predictions are calculated as described in section~\ref{sec:thermal}. As a first observation, one sees that for deuterons and \hethree\ both approaches lead to similar predictions and give a reasonable description of the experimental data. However, both approaches show large differences for the \hthreelambda\ caused by the significantly larger size of  \hthreelambda\ with respect to \hethree. As a matter of fact, the only available data point so far shows a better agreement with the thermal+BW model than with the coalescence model. However, some authors argue that the difference to the coalescence model might be explained by a later formation through $\Lambda$s and deuterons~\cite{Zhang:2018euf}. In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production which is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}. The determination of the exact potential enhancement factor is beyond the scope of this paper as it requires at least a rough knowledge of the wave-function, but a factor of two would be expected from only counting the spin states.
